State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editting paper body

% 
% Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, that scale the field basis functions and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$. The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step. At each iteration, the sequence of estimated states is used to update the parameter set, then resulting parameters are used to estimate a new state vector for the next iteration. The procedure stops when the parameters converge. The algorithm is initialised using a bounded random state sequence which guarantees the initial estimated parameter set forms a stable kernel.

>>>>

% 
% Due to the high dimensionality of the brain and the current electrode systems, we can not expect to have more sensors than basis functions.
\section{State and Parameter Estimation}\label{StateAndParameterEstimationSection} In this section we describe the procedure for estimating the states, $\mathbf{x}_t$, that scale the field basis functions and the connectivity kernel parameters, $\boldsymbol \theta$, and the synaptic time constant, $\xi$. The estimation process is a two part iterative algorithm, consisting of the state estimation step followed by the parameter estimation step. At each iteration, the sequence of estimated states is used to update the parameter set, then the resulting parameters are used to estimate a new state vector for the next iteration. The procedure stops when the parameters converge. The algorithm is initialised using a bounded random state sequence which guarantees the initial estimated parameter set forms a stable kernel. \omg{Parham: can you please add to this to include the initialisation of the field?}
